The paper on blockchain front-running

### 2018-09-25 frontrunning/Latex/sections/paper.tex
[frontrunning] more fixes, separate appendix from main

\subsection{Crypto-Collectibles Games}

@@

The final category in Table~\ref{tab:top25DApps} is name services, which are primarily aimed at displacing central parties involved in web domain registration (\eg ICAAN and registrars) and resolution (\eg DNS). For simple name services (such as some academic work like Ghazal~\cite{moosavighazal}), domains purchases are transactions and network monitors can front-run other users attempting to register domains. This parallels front-running attacks seen in regular (non-blockchain) domain registration~\cite{sac022en33:online}. \textsf{Ethereum Name Service (ENS)}\footnote{\url{https://ens.domains/}} is the most active naming service on Ethereum. Instead of allowing new  \texttt{.eth} domain names to be purchased directly, they are put up for a sealed bid auction. \textblue{Although sealed auction method is used in ENS implementation, the normal workflow uses \texttt{startAuctionsAndBid()} with the deposit equal or higher than the bid, this information leakage could be used to front-run the transaction with the same bid amount or slightly higher to outbid the initial sealed bid. By doing so the front-runner invalidates the original bid and hence registers the domain name himself.}

%too dense. need more explanation. --> explain what sealed auction is? whatsealed mean, refer to cryptokitties. what is actually bein auctions who deposits and what.  how ens actually works . 
% two ways to add bid to an auction, start an auction and bid. but otehr method is that. whta sealed mean, domain is sealed but not anything else.  ENS auction details and then say . 
%same price the first transaction would win, front-running. 
%explain more on ENS auction

@@

\item \emph{Disincentivizing Front-running Actors:} The call market solution also pivots profitable gains that front-running miners stand to gain into fees that they collect~\cite{clark2014decentralizing}, removing the financial incentive to front-run. To the same end, Malinova~\cite{malinova2017market} propose a design for a decentralized exchange which uses economic models in their trading market design to make front-running expensive and more costly than profitable. \textblue{this is what it does, how does it do it?}
% make it more obvious how they do this. how they changed it

%find a home for localethereum. explain the scenario where this actually works, how it can be front-run in original scenario, how this prevents front-running.
\item \emph{\textblue{Technique}:} LocalEthereum, an escrow-based exchange, uses challenge random values from the website to be included in the signature of the transaction (See Code ~\ref{code:localethereum} in Appendix~\ref{app:code}), hence removing any possibility of replay attack or the possibility of any other address modifying key information in the order. \textblue{how does this solve front-running?}

 \end{compactlist}

@@

%Proof of burn methods ?

>>>>

\subsection{Crypto-Collectibles Games}\label{sec:cryptogames}

@@

The final category in Table~\ref{tab:top25DApps} is name services, which are primarily aimed at displacing central parties involved in web domain registration (\eg ICAAN and registrars) and resolution (\eg DNS). For simple name services (such as some academic work like Ghazal~\cite{moosavighazal}), domains purchases are transactions and network monitors can front-run other users attempting to register domains. This parallels front-running attacks seen in regular (non-blockchain) domain registration~\cite{sac022en33:online}. \textsf{Ethereum Name Service (ENS)}\footnote{\url{https://ens.domains/}} is the most active naming service on Ethereum. Instead of allowing new \texttt{.eth} domain names to be purchased directly, they are put up for a sealed bid auction which seals the domain name in the bids, but not the bid amount. The common way of getting a domain is to call \texttt{startAuctionsAndBid()} in ENS auction smart contract, which leaks the hash of the domain name and the initial bid amount in the auction. Users are allowed to bid for 48 hours before the 48-hour reveal phase begins, in which bidders must send a transaction to reveal their bids for a specific domain in auction. It is possible for user to front-run other reveal bids with the same bid amount or slightly higher to outbid the initial sealed bid. The auction model is similar to crypto-collectibles auctions in \ref{sec:cryptogames}

\textblue{Although sealed auction method is used in ENS implementation, the normal workflow uses \texttt{startAuctionsAndBid()} with the deposit equal or higher than the bid, this information leakage could be used to front-run the transaction with the same bid amount or slightly higher to outbid the initial sealed bid. By doing so the front-runner invalidates the original bid and hence registers the domain name himself.}

@@

\item \emph{Disincentivizing Front-running Actors:} The call market solution also pivots profitable gains that front-running miners stand to gain into fees that they collect~\cite{clark2014decentralizing}, removing the financial incentive to front-run. To the same end, Malinova~\cite{malinova2017market} propose a design for a decentralized exchange which uses economic models in their trading market design to make front-running expensive and more costly than profitable. They split big investments into smaller ones using intermediaries --liquidity demander-- and liquidity providers to achieve this.

%find a home for localethereum. explain the scenario where this actually works, how it can be front-run in original scenario, how this prevents front-running.
\item \emph{Trusted party:} It is possible to use a central trusted party, to mitigate the risks of front-running on the DApp design. As an example, LocalEthereum, an escrow-based exchange, facilitates the website as the match making service for the exchange orders, and challenge random values from the website to be included in the signature of the transaction (See Code ~\ref{code:localethereum} in Appendix~\ref{app:code}), hence removing any possibility of replay attack or the possibility of any other address modifying key information in the order. This method prevents network observers to be able to make a new transaction with the defined values as the third party will be the final entity approving the transaction.
 \end{compactlist}

@@
